\documentclass[11pt, a4paper]{article}

% --- PACKAGES ---
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{times}
\usepackage{listings}
\usepackage{xcolor}

% --- DOCUMENT METADATA ---
\title{\textbf{3MITM: A Novel Multi-Agent Attack Framework for DevSecOps Simulation}}
\author{Team 3MITM}
\date{November 3, 2025}

% --- BEGIN DOCUMENT ---
\begin{document}

\maketitle

% --- INSERTED SUMMARY ---
\section*{DevSecOps AI Agent — human-readable summary}

\subsection*{The problem}
DevSecOps teams are stuck in a slow, error-prone loop: when a vulnerability appears in production traffic, analysts must manually triage it, figure out the attack vector, write a fix, file a ticket, and alert stakeholders. That manual hand-off creates delays, increases the chance of mistakes, and leaves systems exposed while teams work.

\subsection*{The idea}
An autonomous, local agent that watches live HTTP/HTTPS traffic, finds vulnerabilities in real time, produces secure code fixes, and escalates the issue to the team --- all in seconds.

\vspace{0.5em}
\hrule
\vspace{0.5em}

\subsection*{Solution overview}

The \textbf{DevSecOps AI Agent} is a local proof-of-concept that demonstrates a fully autonomous vulnerability remediation workflow, integrating network interception, AI analysis/remediation, and team coordination, allowing problems to be detected, fixed, and handed off automatically.

\subsection*{How it works}

\begin{itemize}
    \item \textbf{Network interception} --- The agent sits between services and the internet (via \texttt{mitmproxy}), capturing full HTTP request/response pairs (headers, bodies, status codes).
    \item \textbf{AI-powered detection} --- Captured traffic is sent to an AI analysis engine (e.g., \texttt{watsonx.ai}), which looks for issues such as hardcoded credentials, SQL injection, XSS, insecure serialization, and other OWASP Top 10 problems.
    \item \textbf{Auto-generated fixes} --- When a vulnerability is identified, the same model generates production-ready, framework-aware code changes that address the specific flaw.
    \item \textbf{Automated escalation} --- The system creates a detailed Jira ticket containing the analysis and the suggested fix.
    \item \textbf{Real-time alerts} --- Security teams get richly formatted Slack notifications with one-click links to the Jira ticket and action buttons.
\end{itemize}

\subsection*{Who benefits}

\begin{itemize}
    \item \textbf{DevSecOps engineers} --- Dramatically cut the time spent on manual triage and remediation.
    \item \textbf{Security teams} --- Receive immediate, actionable intelligence with ready-made fixes.
    \item \textbf{Developers} --- Get targeted, tested code examples to implement quickly.
    \item \textbf{Compliance officers} --- Gain a full audit trail of detection, analysis, and remediation actions.
\end{itemize}

\subsection*{What makes it different}

Unlike SAST (which requires commits) or WAFs (which only block traffic), this solution operates transparently on live traffic and uses generative AI for framework-specific remediations---merging interception, reasoning, and team workflows into a single autonomous pipeline for proactive security.

\subsection*{Autonomous behavior}

The agent demonstrates true end-to-end autonomy, as it decides severity, proposes remediation strategies, and coordinates external systems (Jira, Slack) without requiring human approval for every step --- thereby shrinking the window between discovery and resolution.

\subsection*{Impact}

In a test, a hardcoded-credential vulnerability was detected, fixed, ticketed, and escalated in under 10 seconds --- a task that would normally consume 15--30 minutes of manual effort. At scale, this reduces exposure time and greatly improves team productivity and organizational security posture.

\vspace{0.5em}
\hrule
\vspace{0.5em}

\section{3MITM: Three Men in the Middle Framework}

\subsection{Novel Multi-Agent Attack Architecture}

The \textbf{3MITM framework} is a novel proof-of-concept demonstrating coordinated, multi-agent MITM attacks. Rather than monolithic attacks, 3MITM orchestrates three specialized agents sequentially to test the DevSecOps AI Agent's detection and remediation capabilities.

\subsection{The Three Agents}

\textbf{Agent 1 -- Reconnaissance:} Intercepts traffic, identifies sensitive parameters, API endpoints, auth schemes, and vulnerability types via regex analysis.

\textbf{Agent 2 -- Injection:} Receives Agent 1 findings, crafts attack payloads across five vectors (credentials, SQL, XSS, deserialization, data exposure), injects while maintaining protocol compliance.

\textbf{Agent 3 -- Exfiltration:} Monitors responses, extracts credentials/tokens/PII via pattern matching, establishes C\&C exfiltration channel.

\subsection{Attack Orchestration}

The orchestration flow: \textbf{Agent 1 (Recon)} $\rightarrow$ \textbf{Agent 2 (Inject)} $\rightarrow$ \textbf{Agent 3 (Exfil)} $\rightarrow$ \textbf{Defense}. Each agent specializes: reconnaissance identifies vulnerabilities, injection crafts tailored payloads, exfiltration extracts data, then all attack data is forwarded to Flask API.

\subsection{Five Attack Vectors (OWASP-Mapped)}

\begin{itemize}
    \item \textbf{Hardcoded Credentials (A02):} Tokens/passwords from headers
    \item \textbf{SQL Injection (A03):} \texttt{' OR '1'='1} payloads
    \item \textbf{XSS (A03):} \texttt{<script>} tags for cookie theft
    \item \textbf{Insecure Deserialization (A08):} Gadget chain exploitation
    \item \textbf{Data Exposure (A01):} Unencrypted PII extraction
\end{itemize}

\subsection{Defense Integration \& Results}

All attacks detected by Flask API, classified by AI (type, severity, components), remediation code generated, then Jira tickets and Slack alerts created automatically. Validation: 100\% detection (5/5 attacks detected and remediated).

\subsection{Performance Metrics}

\begin{itemize}
    \item \textbf{Total Attacks:} 5 | \textbf{Agents/Attack:} 3 | \textbf{Detection:} 100\%
    \item \textbf{Jira Tickets:} 5 | \textbf{Slack Alerts:} 5 | \textbf{Time:} $\approx 50$ sec
    \item \textbf{Agent 1:} Identified $15+$ sensitive parameters
    \item \textbf{Agent 2:} 100\% injection success rate  
    \item \textbf{Agent 3:} Extracted 5+ datasets, C\&C communication maintained
\end{itemize}

\subsection{Why 3MITM Matters}

3MITM validates AI-powered defense systems detecting sophisticated coordinated attacks. The framework moves beyond SAST and WAFs to operate on live traffic with generative AI remediations, demonstrating autonomous security-as-code at enterprise scale---detecting, remediating, and escalating threats in under a minute.

\end{document}
